---
title: "Lab 02 - Take a sad plot and make it better"
author: "Group Members: Lucas, Ella , Alejandra and Kirsty"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
staff <- read_csv("data/instructional-staff.csv")
```


--------


Team member 1 should pull to download updates and begins here.



### Exercise 1

55 rows



--------

Team member 2 should pull to download updates and begins here.

### Exercise 2

```{r staff-long-create}
# uncomment and edit the code below
staff_long <- staff %>%
  pivot_longer(
    cols = -faculty_type, 
    names_to = "year",
    values_to = "Percentage hire"
    )
```


### Exercise 3

Yes there is 55 rows

```{r staff-long-inspect}
# remove this comment and add your code here

```


Team member 2 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 3 should pull to download updates and begins here.


### Exercise 4

You can't see any data.

```{r lineplot-1}
staff_long %>%
  ggplot(aes(x = year, y = `Percentage hire`, color = faculty_type)) +
  geom_line(aes(group = faculty_type)) 


```



### Exercise 5

The part-time faculty employment has increased.
The full-time tenuere-track faculty and full-time tenured faculty employment trends have both decreased.
The graduate student employees and the full-time non-tenure-track faculty employment trends have stayed the same-

```{r lineplot-2}
# remove this comment and add your code here
```


Team member 3 should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 6

*Remove this text and add your answer here.*

```{r lineplot-3}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 7

*Remove this text and add your answer here. No code needed for this exercise!*


### Exercise 8

*Remove this text and add your answer here.*

```{r lineplot-4}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

All team members should pull to download all updates.


